---
title: "MachineLearningAssignment2Plots"
author: "Qingguo Chen"
date: "October 8, 2017"
output: pdf_document
---

```{r}
library(ggplot2)
library(reshape2)
```


Learning curves of  RHC, SA and GA on Breast_Cancer training set
```{r}
irLogs = read.csv("../Assignment2RandomOptimization/src/data/initialRunTrainingLogs.txt")
irLogs_Tall=melt(irLogs,"Iteration",variable.name = "Algorithm",value.name = "SumOfSquaresError")
```


```{r}
png("LearningCurveWithDefaultSettingROsCancer.png",800,500)
  
g = ggplot(irLogs_Tall,aes(Iteration,SumOfSquaresError,group=Algorithm,col=Algorithm))+
  geom_line()+
  ggtitle("Before Parameter Search")+
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4))
    )

print(g)
dev.off()
print(g)
```


Performance curves of SA with different Ts
```{r}
sa_t_p = read.csv("../Assignment2RandomOptimization/src/data/PerformancesOfSAwithTs.txt")
sa_t_p[,"T"] = as.factor(sa_t_p[,"T"])
sa_p_tall=melt(sa_t_p,"T",variable.name = "Train_Test",value.name = "Accuracy")
saTpSummary =aggregate(sa_p_tall["Accuracy"],by =sa_p_tall[c("T","Train_Test")],function(X) c(mean=mean(X),sd=sd(X),N=length(X)) )
saTpSummary=do.call(data.frame,saTpSummary)
names(saTpSummary)[3:5]=c("Accuracy","sd","N")
saTpSummary$se = saTpSummary$sd/sqrt(saTpSummary$N)
```





```{r}
png("StimulatedAnnealingT.png",800,500)
  
g = ggplot(saTpSummary,aes(T,Accuracy,group=Train_Test,col=Train_Test))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Accuracy-se,ymax=Accuracy+se),width=0.2)+
  ylab("Accuracy")+
  scale_y_continuous()+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Training and Test Accuracy of Stimulated Annealing by T")+
  theme(
    legend.position = c(.05, .05),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```
Performance curves of SA with different Coolings
```{r}
sa_c_p = read.csv("../Assignment2RandomOptimization/src/data/PerformancesOfSAwithCoolings.txt")
sa_c_p$Cooling = as.factor(sa_c_p$Cooling)
sa_c_tall=melt(sa_c_p,"Cooling",variable.name = "Train_Test",value.name = "Accuracy")
saCpSummary =aggregate(sa_c_tall["Accuracy"],by =sa_c_tall[c("Cooling","Train_Test")],function(X) c(mean=mean(X),sd=sd(X),N=length(X)) )
saCpSummary=do.call(data.frame,saCpSummary)
names(saCpSummary)[3:5]=c("Accuracy","sd","N")
saCpSummary$se = saCpSummary$sd/sqrt(saCpSummary$N)
```





```{r}
png("StimulatedAnnealingCooling.png",800,500)
  
g = ggplot(saCpSummary,aes(Cooling,Accuracy,group=Train_Test,col=Train_Test))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Accuracy-se,ymax=Accuracy+se),width=0.2)+
  ylab("Accuracy")+
  scale_y_continuous()+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Training and Test Accuracy of Stimulated Annealing by Cooling")+
  theme(
    legend.position = c(.05, .05),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```

Performance curves of GA with different MatingRate
```{r}
ga_mating_p = read.csv("../Assignment2RandomOptimization/src/data/PerformancesOfGAwithMatingRates.txt")
ga_mating_p$MatingRate = as.factor(ga_mating_p$MatingRate)
ga_mating_tall=melt(ga_mating_p,"MatingRate",variable.name = "Train_Test",value.name = "Accuracy")
ga_matingpSummary =aggregate(ga_mating_tall["Accuracy"],by =ga_mating_tall[c("MatingRate","Train_Test")],function(X) c(mean=mean(X),sd=sd(X),N=length(X)) )
ga_matingpSummary=do.call(data.frame,ga_matingpSummary)
names(ga_matingpSummary)[3:5]=c("Accuracy","sd","N")
ga_matingpSummary$se = ga_matingpSummary$sd/sqrt(ga_matingpSummary$N)
```





```{r}
png("GAMatingRate.png",800,500)
  
g = ggplot(ga_matingpSummary,aes(MatingRate,Accuracy,group=Train_Test,col=Train_Test))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Accuracy-se,ymax=Accuracy+se),width=0.2)+
  ylab("Accuracy")+
  scale_y_continuous()+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Training and Test Accuracy of Genetic Algorithm by Mating Rates")+
  theme(
    legend.position = c(.5, .05),
    legend.justification = c("bottom"),
    legend.box.just = "center",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```

Performance curves of GA with different MutationRate
```{r}
ga_mutate_p = read.csv("../Assignment2RandomOptimization/src/data/PerformancesOfGAwithMutationRates.txt")
ga_mutate_p$MutationRate = as.factor(ga_mutate_p$MutationRate)
ga_mutate_tall=melt(ga_mutate_p,"MutationRate",variable.name = "Train_Test",value.name = "Accuracy")
ga_mutateSummary =aggregate(ga_mutate_tall["Accuracy"],by =ga_mutate_tall[c("MutationRate","Train_Test")],function(X) c(mean=mean(X),sd=sd(X),N=length(X)) )
ga_mutateSummary=do.call(data.frame,ga_mutateSummary)
names(ga_mutateSummary)[3:5]=c("Accuracy","sd","N")
ga_mutateSummary$se = ga_mutateSummary$sd/sqrt(ga_mutateSummary$N)
```





```{r}
png("GAMutationRate.png",800,500)
  
g = ggplot(ga_mutateSummary,aes(MutationRate,Accuracy,group=Train_Test,col=Train_Test))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Accuracy-se,ymax=Accuracy+se),width=0.2)+
  ylab("Accuracy")+
  scale_y_continuous()+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Training and Test Accuracy of Genetic Algorithm by Mutation Rates")+
  theme(
    legend.position = c(.5, .05),
    legend.justification = c("bottom"),
    legend.box.just = "center",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```


Performance curves of three ROs on cancer classification

```{r}
ROsCancerP = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfThreeROsForCancers.txt")
ROsCancerP$Nodes = as.factor(ROsCancerP$Nodes)
ROsCancerP$Iteration = as.factor(ROsCancerP$Iteration)

ROsCancerPSummary =aggregate(ROsCancerP["Evaluation"],by =ROsCancerP[c("Algorithm","Iteration","Nodes","TrainTest")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )

ROsCancerPSummary=do.call(data.frame,ROsCancerPSummary)
names(ROsCancerPSummary)[5:7]=c("Accuracy","sd","len")
ROsCancerPSummary$se = ROsCancerPSummary$sd/sqrt(ROsCancerPSummary$len)
ROsCancerPSummary$legend = paste(ROsCancerPSummary$Algorithm,ROsCancerPSummary$TrainTest)
```





```{r}
png("FinalPeformance3ROsCancer.png",800,500)
  
nodeName = c("10"="Number of Hidden Layer Nodes = 10", "80"="Number of Hidden Layer Nodes = 80" )
g = ggplot(ROsCancerPSummary,aes(Iteration,Accuracy,group=legend,col=legend))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Accuracy-se,ymax=Accuracy+se),width=0.2)+
  ylab("Accuracy")+
  scale_y_continuous()+
  facet_grid(.~Nodes,labeller = as_labeller(nodeName))+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Training and Test Accuracy of Three RO Algorithms by Iteration and Hidden layer nodes")+
  theme(
    legend.position = c(.95, .05),
    legend.justification = c("right","bottom"),
    legend.box.just = "center",
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```

Training time and Test time Evaluation

```{r}
ROsCancerPt = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfThreeROsForCancersTime.txt")
ROsCancerPt$Nodes = as.factor(ROsCancerPt$Nodes)
ROsCancerPt$Iteration = as.factor(ROsCancerPt$Iteration)
ROsCancerPt = ROsCancerPt[ROsCancerPt$TrainTest == "train", ]
ROsCancerTimeSummary =aggregate(ROsCancerPt["Time"],by =ROsCancerPt[c("Algorithm","Iteration","Nodes")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )

ROsCancerTimeSummary=do.call(data.frame,ROsCancerTimeSummary)
names(ROsCancerTimeSummary)[4:6]=c("Time","sd","len")
ROsCancerTimeSummary$se = ROsCancerTimeSummary$sd/sqrt(ROsCancerTimeSummary$len)
```





```{r}
png("CancerIterationTime.png",800,500)
  
g = ggplot(ROsCancerTimeSummary[ROsCancerTimeSummary$Nodes==60,],aes(Iteration,Time,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Time-se,ymax=Time+se),width=0.2)+
  ylab("Training Time (seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Training time of Three RO Algorithms\nOn Cancer classification by Iteration with Nodes = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```



```{r}
png("CancerNodeTime.png",800,500)
  
g = ggplot(ROsCancerTimeSummary[ROsCancerTimeSummary$Iteration==60,],aes(Nodes,Time,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Time-se,ymax=Time+se),width=0.2)+
  ylab("Training Time (seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Training time of Three RO Algorithms\nOn Cancer problem by N with max Iteration = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```



Learning curves of  RHC, SA and GA on Breast_Cancer training set using optimized settings
```{r}
bcLogs = read.csv("../Assignment2RandomOptimization/src/data/RunTrainingLogsBreastCancer.txt")
bcLogs_Tall=melt(bcLogs,"Iteration",variable.name = "Algorithm",value.name = "SumOfSquaresError")
```


```{r}
png("LearningCurveWithOptimizedSettingROsCancer.png",800,500)
  
g = ggplot(bcLogs_Tall,aes(Iteration,SumOfSquaresError,group=Algorithm,col=Algorithm))+geom_line()+
  ggtitle("After Parameter Search")+
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4))
    )

print(g)
dev.off()
print(g)
```

Learning curves of  RHC, SA and GA on Breast_Cancer training set using optimized settings
```{r}
bcLogsLessNode = read.csv("../Assignment2RandomOptimization/src/data/RunTrainingLogsBreastCancerWithLessNodes.txt")
bcLogsLessNode_Tall=melt(bcLogsLessNode,"Iteration",variable.name = "Algorithm",value.name = "SumOfSquaresError")
```


```{r}
ggplot(bcLogsLessNode_Tall,aes(Iteration,SumOfSquaresError,group=Algorithm,col=Algorithm))+geom_line()
```


```{r}
FourPeaks = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfFourROsForFourPeaksWithNs.txt")
FourPeaks$Iteration = as.factor(FourPeaks$Iteration)
FourPeaks$N = as.factor(FourPeaks$N)
```

```{r}
png("FourPeaksBoxPlot.png",800,500)
  
g = ggplot(FourPeaks[FourPeaks$Iteration==1000 & FourPeaks$N==300,],aes(reorder(Algorithm, -Evaluation, median),Evaluation, fill = Algorithm))+geom_boxplot()+scale_x_discrete("Random Optimization Algorithms")+
  ggtitle("Evaluations of Four RO Algorithms On Four Peaks when Iteration = 1000 and N = 300")+
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```

```{r}
meanFourPeaks = aggregate(FourPeaks["Evaluation"],by =FourPeaks[c("Algorithm","Iteration","N")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanFourPeaks=do.call(data.frame,meanFourPeaks)
names(meanFourPeaks)[4:6]=c("Evaluation","sd","Len")
meanFourPeaks$se = meanFourPeaks$sd/sqrt(meanFourPeaks$Len)
```

```{r}
png("FourPeaksIteration.png",800,500)
  
g = ggplot(meanFourPeaks[meanFourPeaks$N==300,],aes(Iteration,Evaluation,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Evaluation-se,ymax=Evaluation+se),width=0.2)+
  ylab("Evaluation")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On Four Peaks by Iteration with N = 300")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```


```{r}
png("FourPeaksN.png",800,500)
  
g = ggplot(meanFourPeaks[meanFourPeaks$Iteration==1000,],aes(N,Evaluation,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Evaluation-se,ymax=Evaluation+se),width=0.2)+
  ylab("Evaluation")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On Four Peaks by N with max Iteration = 1000")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```




```{r}
FourPeaksT = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfFourROsForFourPeaksWithNsTime.txt")
FourPeaksT$Iteration = as.factor(FourPeaksT$Iteration)
FourPeaksT$N = as.factor(FourPeaksT$N)
meanFourPeaksTime = aggregate(FourPeaksT["TrainingTime"],by =FourPeaksT[c("Algorithm","Iteration","N")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanFourPeaksTime=do.call(data.frame,meanFourPeaksTime)
names(meanFourPeaksTime)[4:6]=c("TrainingTime","sd","Len")
meanFourPeaksTime$se = meanFourPeaksTime$sd/sqrt(meanFourPeaksTime$Len)
```

```{r}
png("FourPeaksIterationTime.png",800,500)
  
g = ggplot(meanFourPeaksTime[meanFourPeaksTime$N==200,],aes(Iteration,TrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=TrainingTime-se,ymax=TrainingTime+se),width=0.2)+
  ylab("Training Time (nano seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of training running time of Four RO Algorithms On Four Peaks by Iteration with N = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```

```{r}
png("FourPeaksNTime.png",800,500)
  
g = ggplot(meanFourPeaksTime[meanFourPeaksTime$Iteration==60,],aes(N,TrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=TrainingTime-se,ymax=TrainingTime+se),width=0.2)+
  ylab("Training Time (nano seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Training time of Four RO Algorithms On 4Peaks by N with max Iteration = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```




```{r}
TSP = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfFourROsForTSP.txt")
TSP$Iteration = as.factor(TSP$Iteration)
TSP$NumberOfPoints = as.factor(TSP$NumberOfPoints)
```

```{r}
png("TSPBoxplot.png",800,500)
  
g =ggplot(TSP[TSP$Iteration==400 & TSP$NumberOfPoints == 80,],aes(reorder(Algorithm, -Evaluation, median),Evaluation, fill = Algorithm))+geom_boxplot()+scale_x_discrete("Random Optimization Algorithms")+
  ylab("Evaluation")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On TSPs at Iteration=400,N = 200")+
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```


```{r}
meanTSP = aggregate(TSP["Evaluation"],by =TSP[c("Algorithm","Iteration","NumberOfPoints")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanTSP=do.call(data.frame,meanTSP)
names(meanTSP)[4:6]=c("Evaluation","sd","len")
meanTSP$se = meanTSP$sd/sqrt(meanTSP$len)
```

```{r}
png("TSPIteration.png",800,500)
  
g = ggplot(meanTSP[meanTSP$NumberOfPoints==80,],aes(Iteration,Evaluation,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Evaluation-se,ymax=Evaluation+se),width=0.2)+
  ylab("Evaluation")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On Traveling Salesman Problem by Iteration with N = 80")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```


```{r}
png("TSPN.png",800,500)
  
g = ggplot(meanTSP[meanTSP$Iteration==400,],aes(NumberOfPoints,Evaluation,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Evaluation-se,ymax=Evaluation+se),width=0.2)+
  ylab("Evaluation")+
xlab("N")+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On Traveling Salesman Problems by Number Of Points (400 iteration)")+
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```




```{r}
TSPt = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfFourROsForTSPTime.txt")
TSPt$Iteration = as.factor(TSPt$Iteration)
TSPt$NumberOfPoints = as.factor(TSPt$NumberOfPoints)
meanTSPTime = aggregate(TSPt["TrainingTime"],by =TSPt[c("Algorithm","Iteration","NumberOfPoints")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanTSPTime=do.call(data.frame,meanTSPTime)
names(meanTSPTime)[4:6]=c("TrainingTime","sd","Len")
meanTSPTime$se = meanTSPTime$sd/sqrt(meanTSPTime$Len)
```

```{r}
png("TSPIterationTime.png",800,500)
  
g = ggplot(meanTSPTime[meanTSPTime$N==60,],aes(Iteration,TrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=TrainingTime-se,ymax=TrainingTime+se),width=0.2)+
  ylab("Training Time (nano seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of train time of Four RO Algorithms On TSP by Iteration with NumberOfPoints = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```



```{r}


png("TSPNTime.png",800,500)
  
g = ggplot(meanTSPTime[meanTSPTime$Iteration==60,],aes(NumberOfPoints,TrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=TrainingTime-se,ymax=TrainingTime+se),width=0.2)+
  ylab("Training Time (nano seconds)")+
xlab("N")+
  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Training time of Four RO Algorithms On TSP by NumberOfPoints with max Iteration = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```


```{r}
COs = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfFourROsForCountONEs.txt")
COs$Iteration = as.factor(COs$Iteration)
COs$N = as.factor(COs$N)
```

```{r}
png("COsBoxPlot.png",800,500)
  
g = ggplot(COs[COs$Iteration==400 & COs$N == 700,],aes(reorder(Algorithm, -Evaluation, median),Evaluation, fill = Algorithm))+geom_boxplot()+scale_x_discrete("Random Optimization Algorithms")+
  ggtitle("Evaluations of Four RO Algorithms On COs at Iteration=400,N = 700")+
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```

```{r}
meanCOs = aggregate(COs["Evaluation"],by =COs[c("Algorithm","Iteration","N")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanCOs=do.call(data.frame,meanCOs)
names(meanCOs)[4:6]=c("Evaluation","sd","len")
meanCOs$se = meanCOs$sd/sqrt(meanCOs$len)
```

```{r}
png("COsIteration.png",800,500)
  
g = ggplot(meanCOs[meanCOs$N ==700,],aes(Iteration,Evaluation,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Evaluation-se,ymax=Evaluation+se),width=0.2)+
  ylab("Evaluation")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On CountOnes by Iteration with N = 700")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```

```{r}
png("COsN.png",800,500)
  
g = ggplot(meanCOs[meanCOs$Iteration==400,],aes(N,Evaluation,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=Evaluation-se,ymax=Evaluation+se),width=0.2)+
  ylab("Evaluation")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Four RO Algorithms On CountONes by N with max Iteration = 400")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)
```



```{r}
COst = read.csv("../Assignment2RandomOptimization/src/data/evaluesOfFourROsForCountONEsTime.txt")
COst$Iteration = as.factor(COst$Iteration)
COst$N = as.factor(COst$N)

meanCOsTime = aggregate(COst["TrainingTime"],by =COst[c("Algorithm","Iteration","N")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanCOsTime=do.call(data.frame,meanCOsTime)
names(meanCOsTime)[4:6]=c("TrainingTime","sd","Len")
meanCOsTime$se = meanCOsTime$sd/sqrt(meanCOsTime$Len)
```

```{r}
png("COsIterationTime.png",800,500)
  
g = ggplot(meanCOsTime[meanCOsTime$N==60,],aes(Iteration,TrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=TrainingTime-se,ymax=TrainingTime+se),width=0.2)+
  ylab("Training Time (nano seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of training time of Four RO Algorithms On CountONes by Iteration with N = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```




```{r}
png("COsNTime.png",800,500)
  
g = ggplot(meanCOsTime[meanCOsTime$Iteration==60,],aes(N,TrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=TrainingTime-se,ymax=TrainingTime+se),width=0.2)+
  ylab("Training Time (nano seconds)")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Training time of Four RO Algorithms On CountONes by N with max Iteration = 60")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```


```{r}
COs$SqaredRootTrainingTime = sqrt(COs$TrainingTime)
meanCOsTime2 = aggregate(COs["SqaredRootTrainingTime"],by =COs[c("Algorithm","Iteration","N")],function(X) c(mean=mean(X),sd=sd(X),len=length(X)) )
meanCOsTime2=do.call(data.frame,meanCOsTime2)
names(meanCOsTime2)[4:6]=c("SqaredRootTrainingTime","sd","Len")
meanCOsTime2$se = meanCOsTime2$sd/sqrt(meanCOsTime2$Len)
```



```{r}
png("COsNTime2.png",800,500)
  
g = ggplot(meanCOsTime2[meanCOsTime2$Iteration==400,],aes(N,SqaredRootTrainingTime,group=Algorithm,col=Algorithm))+geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=SqaredRootTrainingTime-se,ymax=SqaredRootTrainingTime+se),width=0.2)+
  ylab("Sqared Root Training Time")+

  theme(axis.text.x = element_text(angle=90, hjust=1))+
  ggtitle("Evaluations of Training time of Four RO Algorithms On CountONes by N with max Iteration = 400")+
  theme(
    legend.position = c(.05, .95),
    legend.justification = c("left","top"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6),
    axis.text = element_text(size = rel(1.3)),
    axis.title = element_text(size = rel(1.4)),
    plot.title = element_text(size = rel(1.5)))
print(g)
dev.off()
print(g)

```



